---
title: 'codes for: Causal models to estimate the effect of planting date recommendation
  on soybean yield'
date: "2024-01-22"
output: html_document
---

```{r libraries}
library(tidyverse)
library(MatchIt)
library(cobalt)
library(Publish)
library(tableone)
library(marginaleffects)

library(parallel)
library(boot)
```

## Causal model framework

Data: Soybean farmer survey data from 11 states in North Central US Planting date recommendation zones map developed by soybean researchers was used to classify if the observed planting date as optimal or non-optimal

```{r, out.width = "100%", fig.align = "center", echo = FALSE}
# Path to the JPG file
jpg_path <- "outputs/pDate_ArcGis.jpg"

# Display the JPG file
knitr::include_graphics(jpg_path)
```

```{r, out.width = "100%", fig.align = "center", echo = FALSE}

# Path to the DAG file
dag_path <- "outputs/dag_PD_yield.png"

# Display the png file
knitr::include_graphics(dag_path)
```

```{r dag}
library(dagitty)

dag_PD <- dagitty("dag {
Crop_growth -> Harvest_date
Crop_growth -> Yield
Harvest_date -> Yield
NPK_application -> Crop_growth
Planting_Date -> Crop_growth
Planting_Date -> disease_severity
Yield_Environment -> Crop_growth
Yield_Environment -> Yield
disease_severity -> Crop_growth
disease_severity -> Yield
field_condition -> Planting_Date
fungicide_application -> disease_severity
maturity_group -> Crop_growth
maturity_group -> Planting_Date
maturity_group -> Yield
planting_depth -> Crop_growth
row_width -> Crop_growth
seeding_rate -> Crop_growth
soil_pH -> Crop_growth
soil_properties -> Crop_growth
latitude -> Crop_growth
latitude -> Planting_Date
latitude -> maturity_group
longitude -> Crop_growth
longitude -> Planting_Date
longitude -> maturity_group
previous.crop -> Crop_growth
previous.crop -> Planting_Date
}")


#minimal adjustment set
cat("the minimal adjustment set")
adjustmentSets(dag_PD, "Planting_Date", "Yield")
```

Intervention: Adhering to recommended planting date, Treatments:- T=1 : optimal planting, T=0 : Non-optimal planting

```{r load-the-data}
load("data/obsData.RData")
data <- obsData
rm(obsData)

#clean data, remove NA
data_cleaned <- na.omit(data)
head(data_cleaned)
```

```{r PS-formula}
# prepare the baseline vars with all the covariates
baselinevars <- names(dplyr::select(data_cleaned,
                                    !c(yield, PD_yday, P_Rdoy, diff_pd_rpd, Y, A)))

# fullmodel formula 
full.model.formula <- as.formula(paste("Y~ A +", 
                                paste(baselinevars, 
                                      collapse = "+")))
cat('Full model formula: \n')
print(full.model.formula)

# propensity score formula
ps.formula <- as.formula(paste("A~", 
                               paste(baselinevars, collapse = "+")))

cat('PS formula: \n')
print(ps.formula)

cat('\nA is the treatment variable \n A = 1 is optimal planting \n A = 0 is non-optimal planting')

```

```{r PS-full-matching}
# full match
match.obj.full <- matchit(ps.formula, data = data_cleaned,
                     method = "full", 
                     estimand = "ATE")

```

```{r balance-of-matching}
# Plot to show PS score matching 
plot(match.obj.full, type = "jitter", interactive = FALSE)
```

```{r balance-plot}
# balance table
cobalt::bal.tab(match.obj.full, un = TRUE, 
        thresholds = c(m = .1))
# blance plot
cobalt::bal.plot(match.obj.full,  
         var.name = "distance", 
         which = "both", 
         type = "histogram",  
         mirror = TRUE)

# PS score distribution seems to be well adjusted 

```
```{r love-plot}
# love plot
cobalt::love.plot(match.obj.full, binary = "std", 
          thresholds = c(m = .1))

# balance is not good, standardized mean difference of many variable out of range

# need to check for alternate balancing specification
```


```{r alternate-matching}

#Full matching on probit PS, check if the balance will improve
m.out2 <- matchit(ps.formula, data = data_cleaned,
                     method = "full", 
                     distance = "glm",
                     link = "probit")

m.out2

```

```{r balance check}

#balance summary
cobalt::bal.tab(m.out2, un = TRUE, 
        thresholds = c(m = .1))

# balance plot
cobalt::bal.plot(m.out2,  
         var.name = "distance", 
         which = "both", 
         type = "histogram",  
         mirror = TRUE)

# love plot
cobalt::love.plot(m.out2, binary = "std", 
          thresholds = c(m = .1))

# balance improved with Full-matching on probit PS
```

``` {r extract the balance data}
# extract the data 
m.out2.data <- match.data(m.out2)
head(m.out2.data)
```

```{r weight-adjusted-model}
fit.out.matched <- lm(full.model.formula,
                     data = m.out2.data,
                     weights = weights) 

# Effect summary using the outcome model 
adj.fit2 <- Publish::publish(fit.out.matched, digits=1)$regressionTable[2,]
print(adj.fit2)

```

```{r cluster-robust-standard-errors}
# crse = cluster-robust standard error
# effect estimates

#G-computation and ATE estimation (better method)
marginaleffects::avg_comparisons(fit.out.matched,
                variables = "A",
                vcov = ~subclass,
                newdata = subset(m.out2.data, A == 1),
                wts = "weights")

```


``````{r standard-bootstrap-function}
# Bootstrapping following PS matching

boot_fun <- function(data, i) {
  boot_data <- data[i,]
  
  #Do 1:1 PS matching with replacement
  m <- matchit(A ~ latitude + longitude + MG.f + prev.crop.type,
               data = boot_data,
               replace = TRUE)
  
  #Extract matched dataset
  md <- match.data(m, data = boot_data)
  
  #Fit outcome model
  fit <- lm(Y ~ A + latitude + longitude + MG.f + prev.crop.type,
             data = md, weights = weights)
  
  ## G-computation ##
  
  #Estimated potential outcomes under treatment
  p1 <- predict(fit, type = "response",
                newdata = transform(md, A = 1))
  Ep1 <- weighted.mean(p1, md$weights)
  
  #Estimated potential outcomes under control
  p0 <- predict(fit, type = "response",
                newdata = transform(md, A = 0))
  Ep0 <- weighted.mean(p0, md$weights)
  
  # Difference
  return(Ep1 - Ep0)
}
```

```{r standard-bootstrap-estimates-no-treatment-covariate-interactions}
## linear model, no treatment-covariate interactions

# Using bootstraps for confidence intervals 
library("boot")
set.seed(54321)
boot_out <- boot(data_cleaned, boot_fun, R = 1999)

boot_out

boot.ci(boot_out, type = "perc")
#ORDINARY NONPARAMETRIC BOOTSTRAP
boot_out

#problematic bootstrapped CI is 0.

# trying different type of distribution, normal distribution
CI1 <- boot.ci(boot_out, type = "norm")  
CI1

# trying percentile
CI2 <- boot.ci(boot_out, type = "perc")
CI2
``` 