---
title: 'codes for: Causal models to estimate the effect of planting date recommendation
  on soybean yield'
date: "2024-01-22"
output: html_document
---

```{r libraries}
library(tidyverse)
library(MatchIt)
library(cobalt)
library(Publish)
library(tableone)
library(marginaleffects)

library(parallel)
library(boot)
```

## Causal model framework

Data: Soybean farmer survey data from 11 states in North Central US Planting date recommendation zones map developed by soybean researchers was used to classify if the observed planting date as optimal or non-optimal

```{r, out.width = "100%", fig.align = "center", echo = FALSE}
# Path to the JPG file
jpg_path <- "outputs/pDate_ArcGis.jpg"

# Display the JPG file
knitr::include_graphics(jpg_path)
```

Intervention: Adhering to recommended planting date, Treatments:- T=1 : optimal planting, T=0 : Non-optimal planting

```{r load-the-data}
load("data/obsData.RData")
data <- obsData
rm(obsData)

#clean data, remove NA
data_cleaned <- na.omit(data)
head(data_cleaned)
```

```{r PS-formula}
# prepare the baseline vars with all the covariates
baselinevars <- names(dplyr::select(data_cleaned,
                                    !c(yield, PD_yday, P_Rdoy, diff_pd_rpd, Y, A)))

# fullmodel formula 
full.model.formula <- as.formula(paste("Y~ A +", 
                                paste(baselinevars, 
                                      collapse = "+")))
cat('Full model formula: \n')
print(full.model.formula)

# propensity score formula
ps.formula <- as.formula(paste("A~", 
                               paste(baselinevars, collapse = "+")))

cat('PS formula: \n')
print(ps.formula)

cat('\nA is the treatment variable \n A = 1 is optimal planting \n A = 0 is non-optimal planting')

```

```{r PS-full-matching}
# full match
match.obj.full <- matchit(ps.formula, data = data_cleaned,
                     method = "full", 
                     estimand = "ATE")

```

```{r balance-of-matching}
# Plot to show PS score matching 
plot(match.obj.full, type = "jitter", interactive = FALSE)
```

```{r balance-plot}
# balance table
cobalt::bal.tab(match.obj.full, un = TRUE, 
        thresholds = c(m = .1))
# blance plot
cobalt::bal.plot(match.obj.full,  
         var.name = "distance", 
         which = "both", 
         type = "histogram",  
         mirror = TRUE)

# PS score distribution seems to be well adjusted 

```
```{r love-plot}
# love plot
cobalt::love.plot(match.obj.full, binary = "std", 
          thresholds = c(m = .1))

# balance is not good, standardized mean difference of many variable out of range

# need to check for alternate balancing specification
```


```{r alternate-matching}

#Full matching on probit PS, check if the balance will improve
m.out2 <- matchit(ps.formula, data = data_cleaned,
                     method = "full", 
                     distance = "glm",
                     link = "probit")

m.out2

```

```{r balance check}

#balance summary
cobalt::bal.tab(m.out2, un = TRUE, 
        thresholds = c(m = .1))

# balance plot
cobalt::bal.plot(m.out2,  
         var.name = "distance", 
         which = "both", 
         type = "histogram",  
         mirror = TRUE)

# love plot
cobalt::love.plot(m.out2, binary = "std", 
          thresholds = c(m = .1))

# balance improved with Full-matching on probit PS
```

``` {r extract the balance data}
# extract the data 
m.out2.data <- match.data(m.out2)
head(m.out2.data)
```

```{r weight-adjusted-model}
fit.out.matched <- lm(full.model.formula,
                     data = m.out2.data,
                     weights = weights) 

# Effect summary using the outcome model 
adj.fit2 <- Publish::publish(fit.out.matched, digits=1)$regressionTable[2,]
print(adj.fit2)

```

```{r cluster-robust-standard-errors}
# crse = cluster-robust standard error
# effect estimates

#G-computation and ATE estimation (better method)
marginaleffects::avg_comparisons(fit.out.matched,
                variables = "A",
                vcov = ~subclass,
                newdata = subset(m.out2.data, A == 1),
                wts = "weights")

```


``````{r standard-bootstrap-function}
boot_fun <- function(data, i, my.fmla) {
  boot_data <- data[i, ]
  
  # Do 1:1 PS matching with replacement:
  m <- matchit(ps.formula, 
               data = boot_data,
               replace = TRUE)
  
  # Extract matched dataset
  md <- match.data(m, data = boot_data)
  
  # Fit outcome model
  fit <- lm(my.fmla,
            data = md, weights = weights)
  
  ## G-computation ##
  # Estimated potential outcomes under treatment
  p1 <- predict(fit, 
                newdata = transform(md, A == 1))
  Ep1 <- weighted.mean(p1, md$weights)
  
  # Estimated potential outcomes under control
  p0 <- predict(fit, type = "response",
                newdata = transform(md, A == 0))
  Ep0 <- weighted.mean(p0, md$weights)
  
  # Debugging: Print potential outcomes
  print(paste("Ep1:", Ep1, "Ep0:", Ep0))
  
  
  # Difference
  return(Ep1 - Ep0)
}
```

```{r standard-bootstrap-estimates-no-treatment-covariate-interactions}
## linear model, no treatment-covariate interactions

# Set up for parallel processing:
library("boot")
set.seed(54321)
# Using bootstraps for confidence intervals 
boot_out <- boot(data_cleaned, boot_fun, my.fmla = full.model.formula, R = 50)

#ORDINARY NONPARAMETRIC BOOTSTRAP
boot_out

#problematic bootstrapped CI is 0.

# trying different type of distribution, normal distribution
CI1 <- boot.ci(boot_out, type = "norm")  
CI1

# trying percentile
CI2 <- boot.ci(boot_out, type = "perc")
CI2
``` 